%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Nikhil Tomar} \\ \vspace{2pt}
    \small +91 9528705553 $|$ \href{mailto:nikt3000@gmail.com}{\underline{nikt3000@gmail.com}} $|$ \href{mailto:cs24b1041@iiitr.ac.in}{\underline{cs24b1041@iiitr.ac.in}} \\ \vspace{2pt}
    \href{https://www.linkedin.com/in/nikhil-tomar-064343242}{\underline{linkedin.com/in/nikhil-tomar-064343242}} $|$
    \href{https://github.com/NIXININE}{\underline{github.com/NIXININE}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Raichur}{Raichur, Karnataka}
      {B.Tech in Computer Science and Engineering; \textbf{CGPA: 8.30}}{Aug. 2024 -- May 2028}
      \resumeItemListStart
        \vspace{2pt}\resumeItem{\textbf{Relevant Coursework:} Design and Analysis of Algorithms, Computer Architecture and Organization, Probability, Data Warehousing, Database Management Systems, Operating Systems, Compiler Design}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Leadership \& Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Core Member, Mathematics Club}{Aug. 2025 -- Present}
      {Indian Institute of Information Technology Raichur}{Raichur, Karnataka}
      \resumeItemListStart
        \resumeItem{Typeset weekly mathematics problem using LaTeX, ensuring precise mathematical notation and professional document formatting for club members.}
        \resumeItem{Organized and executed the evening rapid fire quiz for Pi Day 2026}
        \resumeItem{Collaborated on the publication of the semesterly mathematics magazine, assisting with content curation, proofreading complex equations, and finalizing the digital layout using Canva.}
      \resumeItemListEnd

    \resumeSubheading
      {Core Member, Cybersecurity Club}{Feb. 2025 -- Present}
      {Indian Institute of Information Technology Raichur}{Raichur, Karnataka}
      \resumeItemListStart
        \resumeItem{Actively participate in club activities and contribute to the planning of cybersecurity-focused events and workshops}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects \& Research}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{High Capacity Color 2D (HCC2D) QR Code Implementation} $|$ \emph{C/C++}}{Jan. 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Conceptualized and created an implementation of HCC2D QR codes utilizing different color spectrums}
            \resumeItem{Successfully increased data density compared to standard black-and-white QR codes using C/C++}
          \resumeItemListEnd
      \resumeProjectHeading
       {\textbf{GigTrust} $|$ \emph{Flutter, Rust, JavaScript, Node.js, MongoDB}}{Aug. 2025 -- Dec. 2025}
          \resumeItemListStart
            \resumeItem{Developed a blockchain-based platform for gig workers to ensure fair compensation and trust between employers and employees}
            \resumeItem{Implemented smart contracts in Rust to freeze funds until mutual agreement is reached on the completed work}
            \resumeItem{Built a cross-platform mobile application using Flutter with a backend managed by Node.js and MongoDB}
          \resumeItemListEnd
         
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Python, Rust, JavaScript, SQL, Scheme, Bash, Fish} \\
     \textbf{Frameworks}{: Flutter, Node.js, Ratatui} \\
     \textbf{Developer Tools}{: Git, Docker, Linux} \\
     \textbf{Databases}{: MongoDB, MySQL}
    }}
 \end{itemize}

%-------------------------------------------
